Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-10-13 paper/virtual_cytoplasm_v2.tex
changes in the text

Analyses were done using GROMACS tools after removing artifacts
generated by periodic boundary conditions from the trajectories. A
Mean Square Displacement (MSD) analysis was performed to calculate the
translational diffusion coefficient, which were extracted by a linear
fit to MSD by averaging blocks with a length of $10\, ns$ for dilute systems and $100\, ns$ 
for cytoplasm system~\cite{Allen1987a}. In principle, diffusion
coefficient needs to be corrected for finite size
effects~\cite{Yeh2004} but due to relatively large simulation boxes
this correction is negligible {\bf NOT FOR PROTEINS THAT DIFFUSE
  SLOWLY!}. Root Mean Square Deviation (RMSD) and Root Mean Square
Fluctuation (RMSF) calculations considered the C$\upalpha$ atoms only for analysis in each trajectory
{\bf ARE YOU SURE? THE DEFAULT IS TO TAKE THE AVERAGE STRUCTURE. OR DO
  YOU MEAN THE STRUCTURE FOR FITTING?} {\color{blue} I checked and indeed we used the average structure calculated with the second half of the trajectories. I removed "the reference frame for RMSF was the midpoint of the time interval" from the text. The information about the second half of the trajectory is in the previous paragraph, which is about statistics}. The chain interface area of a given oligomer in a given
frame was calculated as the difference between the solvent exposed
surface area (SASA) of the oligomer in that frame and the sum of the
SASAs of each of its chains independently in that same frame. Other
analyses, such as box volume and Radial Distribution Function (RDF),
followed standard procedures.

@@

\subsubsection{Water fraction}
The number of water molecules was calculated according to the desired
biomolecular concentration, which is a parameter of the cytoplasm
model. This number ranges from 300 to 400 g/L in biological systems
such as \textit{E. coli} cytoplasm~\cite{Zimmerman1991}, which {\bf
  WHAT DOES WHICH CORRESPOND TO?}  corresponds to biomolecular
concentrations as high as 40\%~\cite{Ellis2003a}. In our case, we
choose a biomolecular concentration of 30\%, that is, the number of
molecules necessary to reach a ratio of total biomolecular mass to
water mass of 30\% was inserted into the cytoplasm model.

>>>>

Analyses were done using GROMACS tools after removing artifacts
generated by periodic boundary conditions from the trajectories. A
Mean Square Displacement (MSD) analysis was performed to calculate the
translational diffusion coefficient, which were extracted by a linear
fit to MSD by averaging blocks with a length of $10\, ns$ for dilute systems and $100\, ns$ 
for cytoplasm system~\cite{Allen1987a}. In principle, diffusion
coefficient needs to be corrected for finite size
effects~\cite{Yeh2004} but due to relatively large simulation boxes
this correction is negligible {\bf NOT FOR PROTEINS THAT DIFFUSE
  SLOWLY!}. {\color{blue} The correcion in Yeh2004 is derived for cubic simulation boxes, in our single molecule simulations we have non-cubic boxes, one needs to derive the correction from Eq 11 in Yeh2004. My Mathematica skills are rusty now, could you do that? If you think it's absolutely necessary} Root Mean Square Deviation (RMSD) and Root Mean Square
Fluctuation (RMSF) calculations considered the C$\upalpha$ atoms only for analysis in each trajectory
{\bf ARE YOU SURE? THE DEFAULT IS TO TAKE THE AVERAGE STRUCTURE. OR DO
  YOU MEAN THE STRUCTURE FOR FITTING?} {\color{blue} I checked and indeed we used the average structure calculated with the second half of the trajectories. I removed "the reference frame for RMSF was the midpoint of the time interval" from the text. The information about the second half of the trajectory is in the previous paragraph, which is about statistics}. The chain interface area of a given oligomer in a given
frame was calculated as the difference between the solvent exposed
surface area (SASA) of the oligomer in that frame and the sum of the
SASAs of each of its chains independently in that same frame. Other
analyses, such as box volume and Radial Distribution Function (RDF),
followed standard procedures.

@@

\subsubsection{Water fraction}
The number of water molecules was calculated according to the desired
biomolecular concentration, which is a parameter of the cytoplasm
model. Macromolecular concentration ranges from 300 to 400 g/L in biological systems
such as \textit{E. coli} cytoplasm~\cite{Zimmerman1991}, the highest concentration corresponds to volume occupation as high as 40\%~\cite{Ellis2003a}. In our case, we
choose a biomolecular concentration of 30\%, that is, the number of
molecules necessary to reach a ratio of total biomolecular mass to
water mass of 30\% was inserted into the cytoplasm model.
